peter_plots

### 2024-12-04 peter_plots.qmd
updating plots

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, ".png"), plot = p, width = 6, height = 4)

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, ".png"), plot = p, width = 6, height = 4)

@@

# plot 3:
White/Non-White and importance of race to identity (Q271)

# plot:
White/Non-White and interest in politics (Q29)

@@

print(plot_collegegrad)

@@

print(plot_somecollege)

@@

print(plot_nocollege)

@@

print(plot_collegegrad)

@@

print(plot_somecollege)

@@

print(plot_nocollege)

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, ".png"), plot = p, width = 6, height = 4)

@@

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", race_value, ".png"), plot = p, width = 6, height = 4)

@@

# plot 6:
Rurality and importance of being a member of racial group to identity (Q271)
```{r}

@@

  p <- ggplot(plot_data, aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents in", rural_value, "Areas"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12), 
      plot.title = element_text(size = 14, hjust = 0.5) 
    )

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", race_value, ".png"), plot = p, width = 6, height = 4)

>>>>

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", race_value, "Q29.png"), plot = p, width = 6, height = 4)

@@

# plot 3:
White/Non-White and importance of race to identity (Q271)
```{r}

data_summary <- dataset_clean %>%
  group_by(white, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each education group

plot_whiteQ271 <- data_summary %>% filter(white == "White") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for White Respondents"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_whiteQ271)

plot_nonwhiteQ271 <- data_summary %>% filter(white == "Non-White") %>% ggplot(aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Non-White Respondents"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_nonwhiteQ271)

# plot:
White/Non-White and interest in politics (Q29)
```{r}
data_summary <- dataset_clean %>%
  group_by(white, Q29) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each education group

plot_whiteQ29 <- data_summary %>% filter(white == "White") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for White Respondents"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_whiteQ29)

plot_nonwhiteQ29 <- data_summary %>% filter(white == "Non-White") %>% ggplot(aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Non-White Respondents"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  # Format y-axis as percentages
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +   
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12),  # Customize axis text size
      plot.title = element_text(size = 14, hjust = 0.5)  # Center title
    )

print(plot_nonwhiteQ29)

@@

print(plot_collegegradQ271)

@@

print(plot_somecollegeQ271)

@@

print(plot_nocollegeQ271)

@@

print(plot_collegegradQ29)

@@

print(plot_somecollegeQ29)

@@

print(plot_nocollegeQ29)

@@

  # Save each plot as a separate image file (optional)
  #ggsave(paste0("plot_", age_value, "Q271.png"), plot = p, width = 6, height = 4)

@@

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", age_value, "Q29.png"), plot = p, width = 6, height = 4)

@@

# plot 6:
Rurality and importance of being a member of racial group to identity (Q271)
```{r}
data_summary <- dataset_clean %>%
  group_by(rural, Q271) %>%
  summarise(count = n()) %>%
  mutate(proportion = count / sum(count) * 100)  # Calculate proportion for each race

  p <- ggplot(plot_data, aes(x = Q271, y = proportion, fill = Q271)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents in", rural_value, "Areas"), x = "Importance of Race to Identity", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12), 
      plot.title = element_text(size = 14, hjust = 0.5) 
    )

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", rural_value, "Q271.png"), plot = p, width = 6, height = 4)

  # Print the plot 
  print(p)
}
```

@@

  p <- ggplot(plot_data, aes(x = Q29, y = proportion, fill = Q29)) +
    geom_bar(stat = "identity", position = "dodge") +
    labs(title = paste("Proportions for Respondents in", rural_value, "Areas"), x = "Interest in Politics", y = "Proportion", fill = "Rating") + 
    scale_x_discrete(labels = c("1", "2", "3", "4", "5")) +
    scale_y_continuous(labels = scales::percent_format(scale = 1)) +  
    geom_text(aes(label = sprintf("%.0f%%", proportion)),  
              position = position_dodge(width = 0.8),   
              vjust = 1.5,                               
              size = 4,                                  
              color = "white") +  
    theme_minimal() +
    theme(
      axis.text = element_text(size = 12), 
      plot.title = element_text(size = 14, hjust = 0.5) 
    )

  # Save each plot as a separate image file 
  #ggsave(paste0("plot_", rural_value, "Q29.png"), plot = p, width = 6, height = 4)
